Multispecies survey specifications

### 2020-11-03 msSurveysTest.Rmd
selectivity for full annage, now cut to agecl WIP

>>>>

# compare N at age and C at age between standard and ANNAGE outputs
totNageplot <- function(dat, anndat){

    ggplot() +
    geom_line(data=dat, aes(x=time/stepperyr,y=totN, color="Tot N cohorts"), 
              alpha = 5/10) +
    geom_line(data=anndat, aes(x=time/stepperyr,y=totN, color="Tot N annage"), alpha = 5/10) + 
    theme_tufte() +
    theme(legend.position = "top") +
    xlab("model year") +
    ylab("N") +
    labs(colour=scenario.name) +
    facet_wrap(~species, scales="free")
